PANCHANGE_analysis

### 2021-01-18 PANCHANGE_analysis.Rmd
added retrospective prepandemic ttests and glad edgi sensitivity

@@

>>>>

# GAD retro GLAD and EDGI sensitivity
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment change sensitivity model1b sum_score retro glad edgi sensitivity }
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_retro",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates
# 
# # Regression diagnostic statistics
# gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
#                          explan_var = "gad.sum_score_prepan",
#                          data_set = "dat.prepan")
# kable(gad_prepan_model1b_education_reg_stats)
# gad_prepan_model1b_education_reg_stats
```

@@

# PHQ retro GLAD and EDGI sensitivity
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment change sensitivity model1b sum_score retro in glad edgi sensitivity}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_retro",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates
